---
title: "Calificaciones"
author: "Gutierrez Solis Juan Manuel"
date: "7 de febrero de 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Otoñ0 2013

Programacion Actuarial- 6

Intr. a la Profesion Actuarial- 8

DHPC - 9


Primavera 2014

Teoria del Interes I - 7

Contabilidad General - 8

Formacion Humana y Social - 8

Concepctos de Calculo - 9

Geometria Analitica - 9

Otoño 2014
 
 Teoria del Interes II - 8
 
 Microeconomia - 9
 
 Teoria De Ecuaciones - 9
 
 Primavera 2015
 
 Sistema Financiero Mexicano - 9
 
 Macroeconomia - 9
 
 Matematicas Basicas - 7
 
 Problemas de Mat. Basicas - 7
 
 Otoño 2015
 
 DHTIC - 9
 
 Calculo Diferencial - 9
 
 Algebra Lineal I - 7
 
 Primavera 2016
 
 Demografia I - 8
 
 Derivados Financieros - 6
 
 Reg. Acad. y Cient. del Español - 7
 
 Otoño 2016

Programacion Actuarial II - 8

Legislacion de Seguros - 9

Finanzas Coorporativas - 8

Lengua Extranjera I - 8

Lengua Extranjera II - 8

Lengua Extranjera III - 8
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
